\chapter{Strawmen for Model Building}
\label{ch:strawmen}

In order to develop a model for data volume and data handling it is necessary
to define the duration of one Subrun and the running schedule over the course
of a year.  This chapter specifies strawman models for both.

\section{Strawman Subrun}
\label{sec:strawmanSubrun}

For purposes of this document it is assumed that,
when the accelerator is running,
there will be continuous MI cycles of 1.4~ns for many hours at a time.
Among other things, this means that we are ignoring the possibility of
a few seconds of beam to MTEST approximately once per minute.

A Subrun will be defined as 50 MI~cycles, which has a duration of 70~s.
The transition to the next subrun will occur sometime during the
last off-spill period.

\section{Strawman Year}
\label{sec:strawmanYear}

For purposes of this document it is assumed that the operational plan for
the accelerator complex is:
\begin{enumerate}
  \item 40~weeks per year of accelerator operations; the remaining time will be the yearly accelerator shutdown.
  \item During the accelerator shutdown, Mu2e will take cosmic ray data half of the time
    and will not take data the other half of the time; this time will be used for maintenance, upgrades etc.
  \item When the accelerator is running there will be 20/21 8-hour shifts per week of accelerator operations;
    the other shift is for maintenance and studies.
  \item When the accelerator is delivering beam to the production target, Mu2e will collect data with an
    efficiency of 90\%;
    the other 10\% is an estimate of time lost during run transitions and of time spent resolving technical problems.
    Experience with previous experiments is that 90\% is optimistic.
  \item When Mu2e turns on after a shutdown, it will start taking data immediately at full intensity and full efficiency.
  \item This gives an overall yearly of efficiency of about 66\% for beam data plus an additional 12\% of the year taking
    cosmic ray data during the accelerator shutdown.
\end{enumerate}

